Cards persistent analysis

### 2020-01-08 cards_persistent_analysis.Rmd
Tweaks for dissertation data

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target) %>%
  mutate(expected_reward = expected_reward / max(expected_reward))  # different scalings
```

```{r}
#write_csv()
```

>>>>

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target)
```

```{r}
write_csv(diss_figure_data, "~/Documents/grad/res/psych/cards/analysis/HoMM_data.csv")
```
